\section{Introduction}
\label{sec:introduction}

The Heavy Photon Search experiment probes narrow vector resonances in electroproduced
$e^+e^-$ pairs, with sensitivity driven by precise control of smooth trident
backgrounds and by statistically consistent treatment of detector resolution,
counting fluctuations, and scanning effects \cite{HPS2015DarkPhoton,HPS2016PromptLong,
HPSExperiment2022}. The present workflow replaces earlier piecewise and sideband-window
constructions with a single global Gaussian-process interpolation for each active
dataset, while preserving a narrow blinded interval around every mass hypothesis.

The shift from the earlier piecewise draft to the present global-GP implementation was
motivated by three empirical observations from the HPS validation program. First,
piecewise windowing introduced visible discontinuities in the expected and observed
limit curves near window boundaries. Second, local sideband reconfiguration made
combined results more difficult to interpret when different datasets entered and left
the fit at nearby masses. Third, the global fit naturally supports a shared-$\eps^2$
combination because each dataset provides a single coherent background prediction and
blind-window covariance at every tested mass. The current package therefore performs a
global fit over the full dataset range, excluding only the training window associated
with the signal hypothesis.

This note is written from the current code path rather than the older drafts. In
particular, local significance is based on a profiled Gaussian multi-bin likelihood
ratio, not on the legacy blind-window sum-count approximation retained only for
backward compatibility in utility functions. Similarly, the baseline extraction model
is the additive Gaussian-profiled treatment of GP background uncertainty, while fixed
background and alternative profile choices are discussed only as robustness studies and
future checks.

The document has two goals. The first is to provide a physics-analysis description of
the existing package at a level suitable for internal review and later journal-facing
adaptation. The second is to define an organized Overleaf handoff, with explicit
destination paths for upper-limit, injection/extraction, fit-example, kernel, and
combined-search figures.
