\section{HPS Data Sets and Analysis Scope}
\label{sec:datasets}

\subsection{HPS 2015, 2016, and 2021 data samples}

The present analysis is organized around three HPS running periods: the 2015
engineering run, the 2016 engineering run, and the 2021 physics run. The 2015 and
2016 data were collected with essentially the same detector configuration; in
particular, the engineering-run detector remained under vacuum between those periods,
which makes the two samples especially natural to compare and combine. By contrast, the
2021 run followed the major detector and beam-delivery upgrades described in the later
HPS experiment documentation \cite{HPSExperiment2022}. It therefore represents both a
substantially larger exposure and a distinct detector era.

From the standpoint of statistical workflow, the three samples also play different
roles. The 2015 data remain fully unblinded in the present GPR development chain and
therefore provide the cleanest environment for methodology validation. The 2016 and
2021 samples are treated in staged unblinding steps, consistent with standard HEP
practice: first through development subsets used for fit and toy validation, then
through progressively larger analysis stages once the procedure is frozen.

\begin{table}[H]
\centering
\scriptsize
{\setlength{\tabcolsep}{4pt}
\begin{tabularx}{\linewidth}{@{} P{0.20\linewidth} P{0.11\linewidth} P{0.21\linewidth} P{0.14\linewidth} Y @{}}
\toprule
Data set & Beam energy & Exposure used here & Scan range & Comments \\
\midrule
2015 engineering run &
\SI{1.056}{GeV} &
\SI{1170}{nb^{-1}} &
\SIrange{20}{130}{MeV} &
Published HPS prompt $A^\prime\rightarrow e^+e^-$ search \cite{HPS2015DarkPhoton}. The
published resonance search covered \SIrange{19}{81}{MeV}; the present GPR study is
validated over a wider interval. \\
2016 engineering run\newline (10\% study sample) &
\SI{2.3}{GeV} &
Parent prompt-search exposure:\newline \SI{10608}{nb^{-1}} &
\SIrange{35}{210}{MeV} &
Published HPS prompt and displaced search on the full run \cite{HPS2016PromptLong}. The
current note documents the 10\% subset used for statistical development while retaining
the run-level detector and normalization context of the full sample. \\
2021 physics run\newline (0.03\%, 1\%, and 10\% study stages) &
\SI{3.74}{GeV} &
Full-run luminosity\newline $\sim \SI{160}{pb^{-1}}$ &
\SIrange{35}{230}{MeV} &
Upgraded-detector physics run. The note keeps 0.03\%, 1\%, and 10\% stages explicit so
that the document already matches the intended staged-unblinding sequence. \\
\bottomrule
\end{tabularx}
}
\caption{Summary of the HPS data samples considered in this note. The 2015 and 2016
rows are anchored to published prompt-search results, while the 2021 row records the
physics-run beam energy and approximate delivered luminosity used to organize the later
analysis stages.}
\label{tab:dataset-summary}
\end{table}

\subsection{Mass resolution and the reconstructed invariant-mass spectrum}

The observable entering the statistical analysis is the reconstructed $e^+e^-$
invariant-mass spectrum after the prompt event selection. The narrow signal model is
therefore controlled by the detector mass resolution,
\begin{equation}
\sigma_d(m) = \sum_{k=0}^{N_d} c^{(d)}_k\,m^k,
\end{equation}
with $m$ and $\sigma_d(m)$ expressed in GeV. The current baseline parameterizations are
\begin{align}
\sigma_{2015}(m) &= -9.22283032152\times10^{-5} + 5.32190838657\times10^{-2}\,m, \\
\sigma_{2016}(m) &= 3.8\times10^{-4} + 4.1\times10^{-2}m - 2.7\times10^{-1}m^2
+ 3.49\,m^3 - 11.11\,m^4, \\
\sigma_{2021}(m) &= 2.86957\times10^{-3} - 8.51449\times10^{-3}m + 2.5362319\times10^{-1}m^2.
\end{align}
For 2016, the polynomial is not used unchanged at arbitrarily high mass. The older
parameterization turns over above approximately \SI{180}{MeV} and would imply an
artificial improvement of the mass resolution with increasing mass. To avoid that
unphysical behavior, the current implementation enforces a linear continuation above
$m_0=\SI{0.18}{GeV}$ with slope override \num{0.0239}. This is a technical but
important detail: without it, the width of the signal model would be systematically
underestimated in the upper part of the 2016 search window.

\subsection{Radiative fraction and the \texorpdfstring{$\eps^2$}{epsilon2} normalization}

The radiative fraction encodes the fraction of the selected prompt $e^+e^-$ background
that arises from the purely radiative trident process. This quantity matters because
heavy-photon production in fixed-target experiments is proportional to the radiative
trident rate \cite{EssigEtAl2011,HPS2015DarkPhoton,HPS2016PromptLong}. In the language
used by the published HPS prompt searches,
\begin{equation}
f_{\mathrm{rad}}(m)
= \frac{dN_{\gamma^\ast}/dm}{dN_{\mathrm{bkg}}/dm}
= \frac{dN_{\gamma^\ast}/dm}{dN_{\mathrm{tri}}/dm + dN_{\mathrm{wab}}/dm},
\end{equation}
where $dN_{\gamma^\ast}/dm$ denotes the radiative trident contribution, while the
denominator contains the full physical prompt background after selection. Operationally,
$f_{\mathrm{rad}}$ is determined from Monte Carlo samples of radiative tridents,
tridents, and converted wide-angle Bremsstrahlung passed through the same selection
used for the resonance search. It is therefore not an arbitrary scale factor: it is the
physics quantity that converts the measured prompt spectrum into the rate of the
process most directly analogous to $A^\prime$ production.

For 2015, the present analysis follows the published constant approximation
\begin{equation}
f_{\mathrm{rad},2015}(m) = 0.085.
\end{equation}
For 2016, the earlier bump-hunt notes and the published prompt search used a
mass-dependent fifth-order polynomial extracted from the Monte Carlo composition study.
That parameterization is useful historically and should be discussed as part of the
published methodology, but it becomes unstable above approximately \SI{180}{MeV} and
can grow in a way that is not suitable for the wider GPR search window. The current GPR
analysis therefore adopts the constant approximation
\begin{equation}
f_{\mathrm{rad},2016}(m) = 0.05,
\end{equation}
which is a good representation of the radiative fraction across the selected search
region and avoids the high-mass blow-up of the published polynomial. The 2021
radiative-fraction treatment is retained as provisional in this note pending the final
freeze of the corresponding normalization inputs.

The package now also supports an optional radiative-fraction sensitivity penalty in the
$A \leftrightarrow \eps^2$ conversion. When enabled, the effective radiative fraction
is reduced according to
\begin{equation}
f_{\mathrm{rad},d}^{\mathrm{eff}}(m)
= \left(1-\delta_{f,d}\right) f_{\mathrm{rad},d}(m),
\end{equation}
with dataset-specific penalty fractions configured at the YAML level. The intended
starting point is $\delta_{f,d}=0.07$ for 2015, 2016, and 2021, corresponding to a
7\% sensitivity penalty in the radiative-fraction normalization. Because the bundled
limit figures predate the activation of this switch, the current plots should be read
as pre-penalty results unless stated otherwise.

\subsection{Analysis subsets and staged unblinding}

The current study uses the full 2015 sample, a 2016 10\% development sample, and a set
of progressively larger 2021 study stages. The 2021 0.03\% sample is the first
development subset used for functional-form and GP toy studies. The 2021 1\% sample is
reserved for the first upper-limit and combination campaign, while the 2021 10\% sample
marks the intended first-round unblinding stage. This staged structure is kept explicit
throughout the note because it mirrors the actual analysis strategy rather than merely
the bookkeeping of the current development stage.

The broader statistical motivation for these staged subsets is that the global GP model
is being validated over search windows that are already wider than those used in the
published 2015 and 2016 local-window analyses. That extension is only defensible if the
background model, mass-resolution treatment, and toy-validation program remain stable
across the enlarged mass range. The later sections are organized precisely to document
that validation.
