\section{Event Selection}
\label{sec:event-selection}

The resonance-search workflow begins from histogrammed invariant-mass distributions that
already encode the prompt-selection logic for each run period. The goal of the
selection is to retain prompt $e^+e^-$ pairs that are kinematically consistent with the
electroproduction of a narrow $A^\prime$, while suppressing accidental pairings,
converted wide-angle Bremsstrahlung, and the broad Bethe--Heitler-dominated trident
background that does not share the same prompt-resonance sensitivity as the radiative
trident component.

Several common ideas underlie the selection across all HPS data sets. The analysis uses
well-reconstructed oppositely charged tracks matched to electromagnetic clusters, tight
timing consistency between the two clusters, and momentum and vertex requirements that
favor prompt pair production. These cuts matter for more than detector cleanliness
alone. They directly control the sample composition entering the invariant-mass
spectrum, and therefore they also control the radiative fraction, the mass resolution,
and the background covariance subsequently modeled by the GP.

The distinction between event categories is especially important in the 2016 analysis,
where target-constrained and unconstrained vertex fits play different roles in the
prompt and displaced searches. For the prompt narrow-resonance search, the
target-constrained reconstruction is preferred because it improves the angular and mass
resolution of the $e^+e^-$ pair. That is precisely the category whose invariant-mass
spectrum enters the present GPR note.

The 2015 and 2016 selections shown in Table~\ref{tab:event-selection} are adapted from
the mature HPS prompt-resonance notes and from the earlier analysis drafts that led to
the current statistical workflow. They are sufficiently mature to anchor the present
note. By contrast, the 2021 column is kept deliberately provisional: the row structure
is in place, but several prompt-tight values still need to be synchronized with the
final 2021 reconstruction documentation.

\input{tables/event_selection_table}

The statistical interpretation in the remaining sections assumes that each histogram is
already defined after the corresponding prompt selection. No additional per-event cuts
are introduced by the GP analysis itself. The inference layer consumes only the binned
invariant-mass spectrum together with the dataset-specific scan range, mass resolution,
and radiative-fraction inputs, but all three of those quantities inherit their physical
meaning from the event selection summarized here.
