\begingroup
\small
\setlength{\tabcolsep}{3pt}
\begin{longtable}{@{}P{0.15\linewidth} P{0.27\linewidth} P{0.27\linewidth} P{0.27\linewidth} @{}}
\caption{Compact comparison of prompt-resonance selections. The 2015 and 2016 columns
follow the published/internal engineering-run summaries, while the 2021 column records
the working upgraded-detector 1\% validation subset actually used by the present GPR
workflow. For 2021, the distinction between broad preselection and any later
prompt-tight additions is still being synchronized with the dedicated upgraded-detector
prompt note, so only values already implemented or explicitly tracked in the production
histogram are quoted here.}
\label{tab:event-selection}\\
\toprule
\textbf{Cut type} &
\textbf{2015 (Eng. run 1)} &
\textbf{2016 (Eng. run 2)} &
\textbf{2021 (1\% validation subset)} \\
\midrule
\endfirsthead

\toprule
\textbf{Cut type} &
\textbf{2015 (Eng. run 1)} &
\textbf{2016 (Eng. run 2)} &
\textbf{2021 (1\% validation subset)} \\
\midrule
\endhead

\bottomrule
\endfoot

\bottomrule
\endlastfoot

Trigger / topology &
\Pre pairs-1 trigger; ECAL halves:\newline
$y_{e^+}^{\rm clu}y_{e^-}^{\rm clu}<0$.\newline
\Pro same. &
\Pre Pair1 trigger bit; opposite halves; opposite charge.\newline
\Pro same. &
\Pre current production histogram inherits the upgraded-era opposite-charge
track--cluster pair preselection, but the final note-facing wording is still being
synchronized.\newline
\Pro no additional prompt-only trigger/topology requirement is yet frozen separately in
this note. \\

Track momenta &
\Pre $p(e^-)<0.75\,E_{\rm beam}$.\newline
\Pro $p_{\rm sum}>0.8\,E_{\rm beam}$ and $p_{\rm sum}<1.2\,E_{\rm beam}$. &
\Pre $p(e^\pm)<2.15~\mathrm{GeV}$; $p_{\rm sum}<1.2\,E_{\rm beam}$.\newline
\Pro $p_{\rm sum}>1.90~\mathrm{GeV}$ and $p_{\rm sum}<2.4~\mathrm{GeV}$. &
\Pre $0.4<p(e^-)<2.9~\mathrm{GeV}$ and $0.4<p(e^+)<4.0~\mathrm{GeV}$.\newline
\Pro the production 1\% histogram used here additionally imposes the prompt-tight
requirement $p_{\rm sum}<2.8~\mathrm{GeV}$. \\

Track fit / hits &
\Pre loose track--cluster match:
$\chi^2_{\rm trk-clu}<10$.\newline
\Pro GBL track $\chi^2_{\rm trk}<40$. &
\Pre $\chi^2_{\rm trk}<12$; PID goodness $<10$.\newline
\Pro no additional value stated in the current summary. &
\Pre working upgraded-era values:
$\chi^2_{\rm trk}<20$ and $N_{\rm 2D~hits}\ge10$.\newline
\Pro no separate prompt-tight update is frozen beyond the working production
preselection. \\

Track--cluster timing &
\Pre ---\newline
\Pro $|t_{\rm clu}-t_{\rm trk}-43~\mathrm{ns}|<4.5~\mathrm{ns}$. &
\Pre $|t_{\rm trk}-t_{\rm clu}|<6~\mathrm{ns}$.\newline
\Pro no additional value stated. &
\Pre current upgraded-era production uses working timing windows:
$\Delta t(t_{\rm trk}^{e^-},t_{\rm clu}^{e^+})<6.0~\mathrm{ns}$,
$\Delta t(t_{\rm trk}^{e^+},t_{\rm clu}^{e^+})<5.1~\mathrm{ns}$, and
$\Delta t(t_{\rm trk}^{e^-},t_{\rm clu}^{e^-})<7.8~\mathrm{ns}$.\newline
\Pro no separate prompt-tight timing requirement is frozen beyond the working production
preselection. \\

Cluster--cluster coincidence &
\Pre ---\newline
\Pro $|\Delta t_{\rm clu-clu}|<2~\mathrm{ns}$. &
\Pre $|\Delta t_{\rm clu-clu}|<2~\mathrm{ns}$.\newline
\Pro $|\Delta t_{\rm clu-clu}|<1.43~\mathrm{ns}$. &
\Pre the upgraded-era coincidence requirement is present in the production histogram, but
its final note-facing wording is still being synchronized.\newline
\Pro no additional prompt-tight coincidence value is frozen separately in this note. \\

Vertex / $V_0$ quality &
\Pre if multiple $V_0$ remain, choose the best $\chi^2_{\rm vtx}$.\newline
\Pro $\chi^2_{\rm vtx}<75$ and $p(V_0)<1.2\,E_{\rm beam}$. &
\Pre target-constrained $V_0$ candidates.\newline
\Pro no prompt-tight $\chi^2_{\rm vtx}$ value is stated in the current summary. &
\Pre working upgraded-era values:
$p_{\rm vtx}<4.0~\mathrm{GeV}$ and $\chi^2_{\rm vtx}<20$.\newline
\Pro no separate prompt-tight $V_0$ value is frozen beyond the working production
preselection. \\

Positron cluster energy &
\Pre ---\newline \Pro --- &
\Pre ---\newline \Pro --- &
\Pre working upgraded-era value:
$0.2<E^{\rm clu}_{e^+}<4.0~\mathrm{GeV}$.\newline
\Pro no separate prompt-tight positron-cluster threshold is frozen beyond the working
production preselection. \\

cWAB suppression &
\Pre ---\newline
\Pro $e^+$ must have L1 and L2 hits; $d_0(e^+)<1.1~\mathrm{mm}$; and
$(p_T^- - p_T^+) / (p_T^- + p_T^+) < 0.47$. &
\Pre ---\newline
\Pro not applied in the final 2016 prompt selection summary. &
\Pre the upgraded-era cWAB treatment is still being audited for note integration.\newline
\Pro it has not yet been promoted to a frozen 2021 prompt-baseline entry in this note. \\

Candidate multiplicity &
\Pre unique-$V_0$ policy: keep the best $\chi^2_{\rm vtx}$.\newline
\Pro enforced by the unique-$V_0$ logic. &
\Pre ---\newline
\Pro require a single surviving $V_0$ candidate. &
\Pre the current production histogram applies an upgraded-era unique-candidate policy,
but the exact note-facing wording is still being synchronized.\newline
\Pro no separate prompt-tight multiplicity requirement is frozen beyond that working
policy. \\
\end{longtable}
\endgroup
